%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Cartesi Rollups Builder Bounty} % Affiliation/role
  {myDapp } % Organization/group
  {} % Location
  {Aug. 2024} % Date(s)
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {myDapp is a voting system built on blockchain technology. The
                  application interact with a smart contract to enable
                  consistent and persistent
                  election result. It ensures secure and transparent election
                  process through the
                  blockchain security and enhance voter's trust.}
    \end{cvitems}
  }
%---------------------------------------------------------
  \cventry
  {Personal Project} % Affiliation/role
  {Greenlight } % Organization/group
  {} % Location
  {June. 2024} % Date(s)
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Greenlight is movie api built with go lang.}
      \item {It includes authentication and authorization of users.}
      \item {It employs rate limiting technique to protect and prevent the
                  application from being flooded by numerous service requests.}
      \item {It implement graceful shutdown which allows the OS to perform it's
                  tasks safely after shutting down processes and connections
                  are been closed.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {ADC-Hackathon} % Affiliation/role
  {Will Be There (RSVP) } % Organization/group
  {} % Location
  {Apr. 2024} % Date(s)
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {WillBeThere is an intuitive online RSVP service designed to
                  simplify event organization and attendance tracking.}
      \item {The application enables registered users to effortlessly create
                  events, share event links with friends and easily manage
                  RSVPs to ensure smooth
                  event coordination.}
      \item {Collaborated on the project to develop event dashboard, event
                  creation, event modification modal and implemented the search
                  functionality.}
    \end{cvitems}
  }
  %---------------------------------------------------------
  \cventry
  {Holberton Portfolio Project} % Affiliation/role
  {AnyExam } % Organization/group
  {} % Location
  {Nov. 2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {The goal of this project was to make computer-based exams more
                  user-friendly and accessible for use in recruiting,
                  organizing, and school
                  evaluations. This project is helpful in evaluating applicants
                  throughout the
                  hiring process.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Treblle Hackathon} % Affiliation/role
  {Secure Password Manager API (SAPI) } % Organization/group
  {} % Location
  {Apr. 2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Secure Password Manager API (SAPI) is a server-side application
                  used for password storage, generating passwords, and
                  protecting against
                  password breaches on the internet.}
    \end{cvitems}
  }

  %---------------------------------------------------------
\end{cventries}
