%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


  %---------------------------------------------------------
\cventry
{Fullstack Engineer} % Job title
{Vsured} % Organization
{Nigeria(Remote)} % Location
{Oct. 2024 - } % Date(s)
{
  \begin{cvitems}
    \item {Redesigned Panic Page UI for enhanced user experience and seamless navigation.}
    \item {Integrated backend endpoints for dynamic Panic Page content.} 
    \item {Developed Value-Added Service feature using Remita API for airtime, bill payments, and data purchases.}
    \item {Built scalable application architecture using Express.js/TypeScript (backend) and React/TypeScript (frontend).}
    \item {Integrated API endpoints for dynamic data on multiple pages, improving user experience.}
  \end{cvitems}
}
%---------------------------------------------------------
\cventry
{Fullstack Engineer} % Job title
{Mensa Philosophical Circle} % Organization
{Cyprus(Remote)} % Location
{Aug. 2024 - } % Date(s)
{
  \begin{cvitems}
    \item {Developed responsive web pages for School Owner and Pupil sections, enhancing user engagement.}
    \item {Implemented Notification Module with Push and Email notifications.}
    \item {Integrated multiple payment gateways (Paystack, Remita, Flutterwave, Stripe) for seamless transactions.}
    \item {Built scalable backend using NestJS and TypeScript.}
    \item {Crafted interactive frontend using ReactJS and TypeScript.}
    \item {Created 3D Solar System visualization using Three.js, showcasing innovative expertise.}
  \end{cvitems}
}
%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {VersityEgde} % Organization
    {Ibadan, Nigeria} % Location
    {Aug. 2023 - July. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built fully automated CI/CD pipelines on GitHub for the applications using Github Actions and Azure Virtual Machine.}
        \item {Implemented RESTful API server for blog, forum, and UTME on the go features of the application.}
        \item {Built and deployed overall service infrastructure utilizing Github Actions, and several Microsoft Azure stack(Including Azure Virtual network, Postgresql, Virtual Machine, Azure Static Web application(SWA)), focusing on high-availability, fault tolerance, and auto-scaling.}
        \item {Developed an on-the-go Payment system which can be funded using direct deposits from all banks in Nigeria.}
        \item {Developed a flexible database architecture and design for easy management.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
